Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-11 papers/ms.tex
update ms

\paragraph{Spectra}
We acquired Keck/HIRES spectra for KOI-7913 A on the night of 2021 Nov
13, and KOI-7913 B on the night of 2021 Oct 26.  The
\texttt{SpecMatch-Emp} \citep{yee_SM_2017} machinery yielded $T_{\rm
eff,A} = 4324 \pm 70\,{\rm K}$, $T_{\rm eff,B} = 4038 \pm 70\,{\rm
K}$.  The remaining parameters were in agreement with those from the
cluster isochrone.  For the primary, we also found $[{\rm Fe/H}]=
-0.06 \pm 0.09$, $v\sin i = 13.3 \pm 1.0\,\mkms$, and ${\rm RV}_{\rm
sys} = -17.8 \pm 1.1\,\mkms$.  For the secondary, these same
parameters were $[{\rm Fe/H}]= -0.01 \pm 0.09$, $v\sin i = 10.7 \pm
1.0\,\mkms$, and ${\rm RV}_{\rm sys} = -18.8 \pm 1.1\,\mkms$.  Neither
of the KOI-7913 components shows strong lithium absorption, but this
is expected given their $\approx$K6V and $\approx$K8V spectral types.
They do however both show H$\alpha$ in emission.  We discuss the
significant in greater depth in Appendix~\ref{app:spectra}, but
broadly speaking both observations are consistent with a $\approx$40
Myr age for KOI-7913.

\paragraph{High-Resolution Imaging}
We acquired adaptive optics imaging of KOI-7913 on the night of 2020
Aug 27 using the NIRC2 imager.  The observational configuration and
reduction was identical as before.  The images showed KOI-7913 A,
KOI-7913 B, and an additional faint star $\approx$$0\farcs99$ due East
of KOI-7913 B.  Applying the PSF-fitting routines from
\citet{kraus_impact_2016}, the tertiary star has a separation $\rho =
4397 \pm 3$\,mas from the primary, at a position angle $231.17^\circ
\pm 0.02^\circ$, with a $\Delta K' = 6.97 \pm 0.04$.  While it is too
faint to affect the interpretation of the KOI itself, it would be
amusing if the faint neighbor were also comoving and young -- at the
age of the system, it would have a mass roughly between 10 and
15\,M$_{\rm Jup}$.  Additional imaging epochs will tell.

@@

One weakness of our fitting approach is that we have fixed 5 implicit
parameters per individual transit to their MAP values to remove the
stellar variability signal.  An alternative could be to fit the
planetary transits simultaneously with the starspot-induced
variability using, say, a quasiperiodic Gaussian process (GP).  We
explored this approach, but found that it required careful fine-tuning
of the hyperparameter priors, otherwise the GP would tend to
incorporate variability that was not part of the transit, even if it
was short-term variability attributable to flares, or simply
instrumental noise.  This failure mode is somewhat pernicious, in that
it yields an ill-founded sense of confidence in an ``overly clean''
transit model fit.  While our model is simpler, it has the benefit
that the white noise jitter never trades off with any parameter
equivalent to a damping timescale for the coherence of the GP.  It is
also computationally efficient, and it captures the planetary
parameters that we actually care about.

@@

In the future, it may be possible to obtain independent evidence for
the Cep-Her planets to directly confirm their planetary nature.  The
most likely path would be through transit observations using a
high-resolution spectrograph \citep[see][]{bouma_kep1627_2022}.  In
the interim, it is of interest whether the transit signals could be
astrophysical false positives, or whether they can be argued to be
planetary on a statistical basis.  We adopt the Bayesian framework
implemented in \texttt{VESPA} for this purpose
\citep{morton_efficient_2012,vespa_2015}.  Briefly summarized, the
priors in \texttt{VESPA} take as given the binary star occurrence rate
from \citet{raghavan_survey_2010}, direction-specific star counts from
\citet{girardi_star_2005}, and planet occurrence rates as described by
\citet[][Section~3.4]{morton_efficient_2012}.  The likelihoods are
then evaluated by forward-modeling a synthetic population of eclipsing
bodies for each possible astrophysical model class, in which each
population member has a particular trapezoidal eclipse depth, total
duration, and ingress duration.  These summary statistics are then
compared against the actual photometric data to evaluate the
probabilities of false positive scenarios such as foreground eclipsing
binaries, hierarchical eclipsing binaries, and background eclipsing
binaries.

\paragraph{Kepler-1643}
Kepler-1643~b (KOI-6186.01) was already validated as a transiting
planet by \citet{morton_false_2016}, who found a probability for any
of the aforementioned false positive scenarios of 9$\times$10$^{-6}$.
Repeating the calculation with our own stellar-variability correction
and the new NIRC2 imaging constraints, we find ${\rm FPP} =
6\times10^{-9}$, where the improvement is due to the new NIRC2
contrast curves.  Figure~\ref{fig:planets} shows the justification:
the transit is flat and has a high S/N ($\approx 47$), which is
difficult to reproduce with eclipsing binary models.

@@

\paragraph{KOI-7368}
KOI-7368.01 is listed on the NASA Exoplanet Archive as a ``candidate''
planet.  \citet{morton_false_2016} did not compute a false positive
probability for the system because their default trapezoidal fitting
routine failed, presumably due to the spot-induced variability.  Our
fitting approach rectifies this point, and our new NIRC2 images
revealed no new stellar companions.  Performing the validation
calculation, we find ${\rm FPP} \approx 4\times10^{-3}$.  Though not
as convincing as Kepler-1643, this formally clears the usual threshold
for calling the planet statistically validated
\citep{morton_efficient_2012}.  The S/N of the transit is
$\approx$$32$, which indicates that it is unlikely to be caused by
systematic noise in the light curve (see Figure~\ref{fig:planets}).
The positional probability score also meets the requirements for
transiting sources thought to share positions with their target stars
\citep{morton_false_2016,2017ksci.rept...16B}.

It bears mentioning that KOI-7368 shows a weak centroid shift in the
\texttt{q1\_q17\_dr25\_koi} validation reports, similar to
Kepler-1643.  For KOI-7368, the reported offset is smaller, and less
statistically significant ($0\farcs2$; 3.0-$\sigma$).  Again, the data
validation reports show that the shift is caused by a few outlying
quarters (4, 5, 8, and 12).  The fact that the remaining data show a
consistent scatter between centroid locations suggests that these
outliers are also caused by the stellar variability.  Independently,
our imaging shows that there are no neighboring sources that could
cause an offset of the observed amplitude.

\paragraph{KOI-7913}
KOI-7913.01 is also listed on the NASA Exoplanet Archive as a
``candidate'' planet.  The canonical \citet{morton_false_2016}
analysis was of Q1-Q17 KOIs from DR24, and therefore spanned KOI-1.01
to KOI-7620.01 and omitted KOI-7913.01.  However the results of the
subsequent DR25 analysis by Morton et al.\ are listed at the NASA
Exoplanet Archive.  The relevant table gives a probability for the
system being an astrophysical false positive of $1.4\times10^{-4}$,
with the most likely false positive scenario being a blended eclipsing
binary.  Repeating the calculation with our new detrending and
contrast curves, we find a similar result: ${\rm FPP} =
1.3\times10^{-4}$.  Though the transit has the lowest S/N of any of
the objects discusssed (${\rm S/N}=14$), its lower FPP relative to
KOI-7368 can be understood through its relatively flat-bottomed shape,
combined with its long transit duration relative to plausible
eclipsing binary models (Figure~\ref{fig:planets}).  The host star
probability usability score \citep{2017ksci.rept...16B} also meets the
usual threshold, and so the planet seems to be validated.  Its
disposition has however previously fluctuated from ``false positive''
to ``candidate''.  The most likely explanation is the presence of
KOI-7913~B, which is located approximately one Kepler pixel away from
Kepler-7913 A (see Appendix~\ref{app:koi7913}).  Our pixel-level
analysis of the target pixel files did not show any evidence to
support the idea that KOI-7913~B could host the transiting planet.
Our NIRC2 imaging similarly ruled out the possibility of any other
plausible host star for the planet other than KOI-7913~A.

@@

\subsection{Normal-Sized Mini-Neptunes Exist at 40$\,$Myr}

Current thinking about the origins and evolution of lose-in
mini-Neptunes has recently been reviewed by \citet{bean_nature_2021}.
In the context of the existing exoplanet population, the most
significant novelty about Kepler-1643~b, KOI-7368.01, and KOI-7913 is
that they have normal sizes.
More specifically, the size distribution of mini-Neptunes spans
$\approx$1.8\,$R_\oplus$ to $\approx$3.6\,$R_\oplus$, with a peak at
$\approx 2.4\,R_\oplus$ \citep[][Figure~7]{Fulton_et_al_2017}.
Figure~\ref{fig:rp_period_age} shows the sizes, orbital periods, and ages of
known transiting planets, emphasizing those with precise ages.
Considering planets younger than $10^8$ years, the smallest previously
known were AU~Mic~c ($\approx3.0\pm0.2\,R_\oplus$, averaging the
results of \citealt{martioli_aumicbc_2021} and
\citealt{gilbert_flares_2022}), Kepler-1627~Ab ($3.8\pm0.2\,R_\oplus$;
\citealt{bouma_kep1627_2022}), and AU~Mic~d ($4.2\pm0.2\,R_\oplus$;
\citealt{plavchan_planet_2020}).
The other transiting planets younger than $10^8$ years are much
larger, with sizes between 4 and 10$\,R_\oplus$
\citep{Mann_K2_33b_2016,David_et_al_2017,benatti_possibly_2019,david_four_2019,newton_tess_2019,rizzuto_tess_2020,bouma_cluster_2020}.

%TODO: I think we might need James Owen to contribute something
%similar to the TOI-1227 models?
{\bf Run some evolutionary models, make some comments about the core
	mass, KH timescale, etc}.

\subsection{Is CH-2 really a star cluster?}

RSG-5, and Kepler-1643's membership inside it, clearly meet the
typical expectations of a star claimed to be in an open cluster.
RSG-5 shows an obvious overdensity relative to the local field
population ({\it e.g.}, Figure~\ref{fig:XYZvtang}), and our membership
selection easily produces a clean pre-main-sequence locus in 
color-absolute magnitude space (Figure~\ref{fig:age}).
CH-2, and KOI-7913 and KOI-7368's membership inside it, do not meet
those expectations in as obvious a manner.  This is because this
association of stars is diffuse.

%really 80:9
To quantify the density discrepancy, we can compare the spatial and
velocity volumes searched to select candidate members of each cluster.
For RSG-5, we drew 141 candidate members from a $30\,{\rm
pc}\times30\,{\rm pc}\times30\,{\rm pc}$ spatial cube, given a $1 {\rm \mkms} \times 2 {\rm \mkms }$ rectangle in apparent galactic velocity.
For CH-2, our 37 candidate members came from a spatial cube of
dimension $50\,{\rm pc}\times40\,{\rm pc}\times30\,{\rm pc}$, and the
velocity rectangle of $2 {\rm \mkms} \times 4 {\rm \mkms}$.  If we
define the ``searched volume'' in units of ${\rm pc}^3 {\rm
(\mkms)}^2$, then the volume ratio of CH-2:RSG-5 is $\approx$9:1.  The
density (number of stars per unit searched volume) within RSG-5 relative to
CH-2 similarly comes out to 34 to 1.

So what makes a star cluster?  Historic answers to this question have
recently by reviewed by \citet{krumholz_star_2019}: some definitions
that have been offered include criteria such as being gravitationally
bound, and having a mass density that significantly exceeds the mean
in a cluster's galactic neighborhood.  We prefer a modified version of
the definition adopted by \citet{krumholz_star_2019}: for our purposes
a star cluster is a group of at least 12 stars that was physically
associated at its time of formation.  The somewhat arbitrary ``12'' is
set to distinguish clusters from high-order multiple star systems.  We
therefore explicitly include dissolved clusters and their tidal tails
in our concept of clusters.  We also explicitly exclude the idea that
a particular number of stars per unit spatial volume is required to
define a cluster.  The latter point acknowledges the fact that an
important factor in cluster identification is now also the number per
unit velocity volume, whether in 2-dimensional tangential velocity, or
when including the third radial component.  Perhaps
once stellar rotation periods and chemical abundances reach the same
level of ubiquity as stellar proper motions, they might enable further
refinement of our ability in cluster discovery.

From a data-driven perspective, how do we demonstrate that a star is
in a cluster, {\it i.e.}, that it is part of a group of stars that was
physically associated at its time of formation?
Back-integrating the orbits is one convincing approach, but it does
not always work {\bf (CITE)}.
The relatively minimal approach suggested by \citet{tofflemire_2021}
is intriguing: search for coeval, phase-space neighbors, measure their
ages, and determine if they share a common age.
This approach is more accurately be described as a method for
determining whether a star is currently associated with a set of coeval
stars, which is much easier to determine than what the association
looked like in the past.
From this standard, our analysis thus far of CH-2 has already
demonstrated the existence of such an assocation.

A crucial logical step in this method however is to ensure that the
(automated) search process for coeval phase-space neighbors in fact
produces neighbors at a rate different from what it would for field
stars.

% TODO
And so we ask: what is the density of field stars in the CH-2 region?
If we had applied Ronan's pre-main-sequence selection, + HDBScan, +
local neighbors... what would we have gotten?
Similarly... if you just applied Adam Kraus' Comove 
What is the likelihood we are fooling ourselves?

\subsection{Further Work on Cep-Her}

Disentangling its kinematics
* Need an RV survey.

Benchmarking its age(s):
* Lithium analysis of FGK depletion (bright enough to be feasible).

@@

Finding more interesting objects in it:
* Kepler data... presumably $\sim$200 stars in the cluster were
observed, in order to have detected 4 planets.

* TESS data

>>>>

\paragraph{Spectra}
We acquired Keck/HIRES spectra for KOI-7913 A on the night of 2021 Nov
13, and KOI-7913 B on the night of 2021 Oct 26.  The
\texttt{SpecMatch-Emp} \citep{yee_SM_2017} machinery yielded $T_{\rm
eff,A} = 4324 \pm 70\,{\rm K}$, $T_{\rm eff,B} = 4038 \pm 70\,{\rm
K}$.  The remaining parameters were in agreement with those from the
cluster isochrone.  For the primary, we also found $[{\rm Fe/H}]=
-0.06 \pm 0.09$, $v\sin i = 13.3 \pm 1.0\,\mkms$, and ${\rm RV}_{\rm
sys} = -17.8 \pm 1.1\,\mkms$.  For the secondary, these same
parameters were $[{\rm Fe/H}]= -0.01 \pm 0.09$, $v\sin i = 10.7 \pm
1.0\,\mkms$, and ${\rm RV}_{\rm sys} = -18.8 \pm 1.1\,\mkms$.  Neither
of the KOI-7913 components shows strong lithium absorption, but this
is expected given their $\approx$K6V and $\approx$K8V spectral types.
They do however both show H$\alpha$ in emission.  We discuss the
significance in greater depth in Appendix~\ref{app:spectra}, but
broadly speaking both observations are consistent with a $\approx$40
Myr age for KOI-7913.

\paragraph{High-Resolution Imaging}
We acquired adaptive optics imaging of KOI-7913 on the night of 2020
Aug 27 using the NIRC2 imager.  The observational configuration and
reduction were identical as before.  The images showed KOI-7913 A,
KOI-7913 B, and an additional faint star $\approx$$0\farcs99$ due East
of KOI-7913 B.  Applying the PSF-fitting routines from
\citet{kraus_impact_2016}, the tertiary star has a separation $\rho =
4397 \pm 3$\,mas from the primary, at a position angle $231.17^\circ
\pm 0.02^\circ$, with $\Delta K' = 6.97 \pm 0.04$.  While it is too
faint to affect the interpretation of the KOI itself, it would be
amusing if the faint neighbor were also comoving and young -- at the
age of the system, it would have a mass roughly between 10 and
15\,M$_{\rm Jup}$.  Additional imaging epochs will tell.

@@

One weakness of our fitting approach is that we have fixed 5 implicit
parameters per individual transit to their MAP values to remove the
stellar variability signal.  An alternative could be to fit the
planetary transits simultaneously with the starspot-induced
variability using, say, a quasiperiodic Gaussian process (GP).  We
explored this approach, but found that it required careful fine-tuning
of the hyperparameter priors, otherwise the GP would tend to
incorporate variability that was not part of the transit, even if it
was short-term variability attributable to flares, or simply
instrumental noise.  This failure mode is somewhat pernicious, in that
it yields an ill-founded sense of confidence in an ``overly clean''
transit model fit.  While our model is simpler, it has the benefit
that the white noise jitter never trades off with any parameter
equivalent to a damping timescale for the coherence of the GP.  It is
also computationally efficient, and it captures the planetary
parameters about which we care the most.

@@

In the future, it may be possible to obtain independent evidence for
the Cep-Her planets to directly confirm their planetary nature.  The
most likely path would be through transit observations using a
high-resolution spectrograph.  In
the interim, it is of interest whether the transit signals could be
astrophysical false positives, or whether they can be argued to be
planetary on a statistical basis.  We adopt the Bayesian framework
implemented in \texttt{VESPA} for this purpose
\citep{morton_efficient_2012,vespa_2015}.  Briefly summarized, the
priors in \texttt{VESPA} take as given the binary star occurrence rate
from \citet{raghavan_survey_2010}, direction-specific star counts from
\citet{girardi_star_2005}, and planet occurrence rates as described by
\citet[][Section~3.4]{morton_efficient_2012}.  The likelihoods are
then evaluated by forward-modeling a synthetic population of eclipsing
bodies for each possible astrophysical model class, in which each
population member has a particular trapezoidal eclipse depth, total
duration, and ingress duration.  These summary statistics are then
compared against the actual photometric data to evaluate the
probabilities of false positive scenarios such as foreground eclipsing
binaries, hierarchical eclipsing binaries, and background eclipsing
binaries.

\paragraph{Kepler-1643}
Kepler-1643~b (KOI-6186.01) was already validated as a transiting
planet by \citet{morton_false_2016}, who found a probability for any
of the aforementioned false positive scenarios of 9$\times$10$^{-6}$.
Repeating the calculation with our own stellar-variability correction
and the new NIRC2 imaging constraints, we find ${\rm FPP} =
6\times10^{-9}$, where the improvement is due to the new NIRC2
contrast curves.  Figure~\ref{fig:planets} shows the justification:
the transit is flat and has a high S/N ($\approx 47$).  The shape is
therefore difficult to reproduce with eclipsing binary models.

@@

\paragraph{KOI-7368}
KOI-7368.01 is listed on the NASA Exoplanet Archive as a ``candidate''
planet.  \citet{morton_false_2016} did not compute a false positive
probability for the system because their default trapezoidal fitting
routine failed, presumably due to the spot-induced variability.  Our
fitting approach rectifies this point, and our new NIRC2 images
revealed no new stellar companions.  Performing the relevant
calculation, we find ${\rm FPP} \approx 4\times10^{-3}$.  Though not
as convincing as Kepler-1643, this formally clears the usual threshold
for calling the planet statistically validated
\citep{morton_efficient_2012}.  The S/N of the transit is
$\approx$$32$, which indicates that it is unlikely to be caused by
systematic noise in the light curve (see Figure~\ref{fig:planets}).
The positional probability score also meets the requirements for
transiting sources thought to share positions with their target stars
\citep{2017ksci.rept...16B}.

It bears mentioning that KOI-7368 shows a weak centroid shift in the
\texttt{q1\_q17\_dr25\_koi} validation reports, similar to
Kepler-1643.  For KOI-7368, the reported offset is smaller, and less
statistically significant ($0\farcs2$; 3.0-$\sigma$).  Again, the data
validation reports show that the shift is caused by a few outlying
quarters (4, 5, 8, and 12).  The fact that the remaining data show a
consistent scatter between centroid locations suggests that these
outliers are also caused by the stellar variability.  Independently,
our NIRC2 imaging shows that there are no neighboring sources that
could cause an offset of the observed amplitude.

\paragraph{KOI-7913}
KOI-7913.01 is also currently listed on the NASA Exoplanet Archive as a
``candidate'' planet.  The canonical \citet{morton_false_2016}
analysis was of Q1-Q17 KOIs from DR24, and therefore spanned KOI-1.01
to KOI-7620.01 and omitted KOI-7913.01.  However the results of the
subsequent DR25 analysis by Morton et al.\ are listed at the NASA
Exoplanet Archive.  The relevant table gives a probability for the
system being an astrophysical false positive of $1.4\times10^{-4}$,
with the most likely false positive scenario being a blended eclipsing
binary.  Repeating the calculation with our new detrending and
contrast curves, we find a similar result: ${\rm FPP} =
1.3\times10^{-4}$.  Though the transit has the lowest S/N of any of
the objects discusssed (${\rm S/N}=14$), its lower FPP relative to
KOI-7368 can be understood through its relatively flat-bottomed shape,
combined with its long transit duration relative to plausible
eclipsing binary models (Figure~\ref{fig:planets}).  The host star
probability usability score \citep{2017ksci.rept...16B} also meets the
usual threshold, and so the planet seems to be validated.  Its
disposition has however previously fluctuated from ``false positive''
to ``candidate''.  The most likely explanation is the presence of
KOI-7913~B, which is located approximately one Kepler pixel away from
Kepler-7913 A (see Appendix~\ref{app:koi7913}).  Our pixel-level
analysis of the target pixel files did not show any evidence to
support the idea that KOI-7913~B could host the transiting planet.
Our NIRC2 imaging similarly ruled out the possibility of any other
plausible host star for the planet other than KOI-7913~A.

@@

\subsection{Normal-Sized Mini-Neptunes Exist at 40$\,$Myr}
\label{subsec:sizes}

The most significant novelty about
Kepler-1643~b, KOI-7368.01, and KOI-7913~Ab is that their sizes are
normal, relative to the known population of gigayear-old
mini-Neptunes.  At field star ages, mini-Neptune sizes span
1.8\,$R_\oplus$ to 3.6\,$R_\oplus$, with the most
common size being $\approx 2.4\,R_\oplus$
\citep[][Figure~7]{Fulton_et_al_2017}.  The known planets younger than
$10^8$ years are almost all larger, with sizes between 4 and
10$\,R_\oplus$
\citep{Mann_K2_33b_2016,David_et_al_2017,benatti_possibly_2019,david_four_2019,newton_tess_2019,rizzuto_tess_2020,bouma_cluster_2020,mann_toi1227_2022}.
Figure~\ref{fig:rp_period_age} explores this in more detail by showing
the sizes, orbital periods, and ages of the known transiting planets,
emphasizing planets with precise ages.  The smallest previously known planets
comparable to the new Cep-Her mini-Neptunes
are AU~Mic~c ($3.0\pm0.2\,R_\oplus$, see
\citealt{martioli_aumicbc_2021} and \citealt{gilbert_flares_2022}),
Kepler-1627~Ab ($3.8\pm0.2\,R_\oplus$; \citealt{bouma_kep1627_2022}),
and AU~Mic~d ($4.2\pm0.2\,R_\oplus$; \citealt{plavchan_planet_2020}).

The theoretical expectation is that mini-Neptunes with sizes of 2 to
3\,$R_\oplus$ should be common at ages of $10^7$ to $10^8$ years.
This expectation is tied to inferences about the
initial distributions of planetary core mass, core composition, and
atmospheric mass fraction \citep{owen_evaporation_2017}.  The
Kelvin-Helmholtz cooling timescale, which is tied to the entropy of
the planetary interior once the disk disperses, could also play a
significant role \citep{owen_constraining_2020}.  As an example,
\citet{rogers_unveiling_2021} predicted that given a core-mass
distribution peaked at $\approx$$4$\,M$_\oplus$, an ice-poor rock/iron
core composition, and a typical H/He mass fraction of $\approx$4\%,
there should be a maximum in planet occurrence at 2 to 3\,$R_\oplus$,
at times between 10 and 100\,Myr
(their Figure~16).  The models advanced by
\citet{gupta_signatures_2020} and \citet{lee_primordial_2021} agree;
the theoretical differences lie in their explanations
for the origin of the radius valley.  If the radius gap is primordial
and created by gas accretion physics, then super-Earths
($<$$1.8$\,$R_\oplus$) would be common as early as $10^7$ years
\citep{lee_primordial_2021}.   The photoevaporation-driven models more
often quote $10^8$ year timescales for production of
atmosphere-stripped super-Earths, while the models with the mass-loss
driven by a slow escape of heat from the core predict longer
$\sim$$10^9$ year timescales (but see \citealt{king_euv_2020}).

Systems such as K2-25, V1298~Tau, HIP-67522, TOI-837,
and TOI-1227 have sizes that are much larger than the picture we have
just described.  However, their large sizes can be accommodated
by existing models by invoking any of {\it i)} larger core masses,
{\it ii)} more volatile-rich compositions, {\it iii)}  larger initial
atmospheric mass fractions, or {\it iv)} longer thermal cooling times.
For instance, perhaps all five of the the aforementioned systems are
large simply because the planets are more massive than most
mini-Neptunes.  Secure mass measurements would help constrain this
parameter space, but the $\sim$1\,\kms\ spot-induced radial velocity
semi-amplitudes makes measuring the Doppler orbits incredibly
challenging.  \citep[][]{cale_diving_2021,zicher_one_2022,klein_one_2022}.
Regardless, the new Kepler-1643, KOI-7368, and KOI-7913 systems do
demonstrate that at least some planets at 40\,Myr have sizes that are
consistent with theoretical expectations for mini-Neptunes.  While
selection effects imposed by spot-induced photometric variability are
a likely explanation for why planets this small have not previously
been identified \citep[{\it e.g.},][]{zhou_2021_tois}, future work
should quantify this bias more carefully, in order to enable empirical
studies of how the planetary size distribution changes at early times.

\subsection{Is CH-2 a real cluster?}
\label{subsec:ch2}

RSG-5, and Kepler-1643's membership inside it, meet typical
expectations for a star claimed to be in an open cluster.  RSG-5 is an
obvious overdensity relative to the local field, and our
membership selection easily produces a clean pre-main-sequence locus
in color versus absolute magnitude (Figure~\ref{fig:age}).  CH-2, and
KOI-7913 and KOI-7368's membership inside it, do not meet these
expectations in as obvious a manner.  This is because the CH-2
association is diffuse.

To quantify the density difference between CH-2 and RSG-5, we can compare the spatial and
velocity volumes searched for each group.
For RSG-5, we drew 141 candidate members from a $30\,{\rm
pc}\times30\,{\rm pc}\times30\,{\rm pc}$ spatial cube, given a $1 {\rm
\mkms} \times 2 {\rm \mkms }$ rectangle in apparent galactic velocity.
For CH-2, our 37 candidate members came from a rectangular prism of
dimension $50\,{\rm pc}\times40\,{\rm pc}\times30\,{\rm pc}$, and a
rectangular box of $2 {\rm \mkms} \times 4 {\rm \mkms}$.  If we define
the searched volume in units of ${\rm pc}^3\,{\rm km^2}\,{\rm s^{-2}}$, then
the volume ratio of CH-2 to RSG-5 is 9 to 1.  The number of candidate
members per unit searched volume in RSG-5 relative to CH-2 is
therefore 34 to 1.

Given its low density, in CH-2 really a star cluster?  For this
discussion, let us adopt the definition that a star cluster is a group
of at least 12 stars that was physically associated at its time of
formation.  The somewhat arbitrary ``12'' is set to distinguish star
clusters from high-order multiples \citep[see][]{krumholz_star_2019}.
Dissolved clusters and their tidal tails are therefore included in our
concept of clusters.  We do not require however that a particular number of stars per
unit spatial volume is required for a group to be a ``cluster''.
The latter point acknowledges that an important
factor in cluster identification is also the density in velocity
space.  Perhaps once stellar rotation periods and chemical abundances
reach the same level of ubiquity as stellar proper motions, they might
enable further refinement of our ability to discover stars that formed
together.

From a data-driven perspective, demonstrating that a group of stars
was physically associated at its time of formation is challenging.
While some young groups show kinematic evidence for expansion
\citep{kuhn_kinematics_2019}, many, including Sco-Cen, do not
\citep{wright_kinematics_2018}.  This complicates the feasibility of
deriving kinematic ages through traceback, as
well as through the expansion itself
\citep[see][]{crundall_chronostar_2019}.  A more minimal approach is
that suggested by \citet{tofflemire_2021}: search for coeval,
phase-space neighbors, measure their ages, and determine if they share
a common age.  This approach can demonstrate whether a star is {\it
currently associated} with a set of coeval stars, which is much easier
than determining what the association looked like in the past.  Our
analysis of CH-2 meets the latter standard for the existence of a
$\approx$40\,Myr assocation today.  It would be a worthy exercise for
future work to perform a similar search for coeval phase-space
neighbors on the entire dataset of known exoplanet hosts.  For the
time being, we can offer the anecdotal point that in our experience,
most stars do not have dozens of $\sim$40\,Myr neighbors within a
local volume of a few \kms\ and tens of parsecs.

\subsection{Future work}

\subsubsection{Cep-Her}
\paragraph{Kinematics}
* Need an RV survey.

\paragraph{Age(s)}
Benchmarking its age(s):
* Lithium analysis of FGK depletion (bright enough to be feasible).

@@

\paragraph{More objects}

* TESS data: giant planets in Cep-Her.  We need more 1e7-1e8 year old
stars for the HJ occurrence versus time question.  This will help.

* Kepler data: exocomets?  Search for smaller planets?

\subsubsection{Occ rates}
* Kepler data... presumably $\sim$200 stars in the cluster were
observed, in order to have detected 4 planets. 
Occurrence rates?
